%----------------------------------------%

% Jagger Harris's Resume
% Last modified on 06/09/22

%----------------------------------------%

\documentclass[letterpaper,11pt]{article}

% Packages
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{latexsym}
\usepackage{marvosym}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{verbatim}

\usepackage[english]{babel}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage[hidelinks]{hyperref}

\usepackage{fontawesome5}

% Fix page width
\usepackage[scale=0.90,lf]{FiraMono}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Jagger Harris Resume},
    pdfpagemode=FullScreen,
}

% Light gray color %%
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

% Custom underline %
\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}


% Custom font
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault} 
% Only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat {\section}{
    \bfseries \vspace{-6pt} \raggedright \large % header section
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-4pt}]

% Only used for PDFLatex
% Ensure that generate pdf is machine readable/ATS parsable
% \pdfgentounicode=1

%----------------------------------------%

% Custom commands

%----------------------------------------%

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\ % top row of resume entry
      \textit{#3} & {\color{dark-grey} \small #4}\vspace{1pt}\\ % second row of resume entry
      & \color{dark-grey} \small #5
    \end{tabular*}\vspace{-20pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\color{dark-grey}} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeExtracurricularsHeading}[1]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\color{dark-grey}} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% Set default leftmargin to 0.15 in
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}\setlength{\itemindent}{-1em}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\color{text-grey}

%----------------------------------------%

% RESUME DOCUMENT %

%----------------------------------------%

\begin{document}

% Heading %
\begin{center}
	\textbf{\Huge Jagger Harris} \\ \vspace{5pt}
	\small \faPhone* \texttt{\href{tel:+1555-555-5555}{555-555-5555}} \hspace{1pt} $|$
  %\small \faPhone* \texttt{555-555-5555} \hspace{1pt} $|$
	\hspace{1pt} \faEnvelope \hspace{2pt} \texttt{\href{mailto:jagger.lee.harris@gmail.com}{jagger.lee.harris@gmail.com}} \hspace{1pt} $|$
	\hspace{1pt} \faGithub \hspace{2pt} \texttt{\href{https://github.com/jagger-harris}{jagger-harris}} \hspace{1pt} $|$
	\hspace{1pt} \faLinkedin \hspace{2pt} \texttt{\href{https://www.linkedin.com/in/jagger-harris/}{jagger-harris}} \hspace{1pt}
	\\ \vspace{-3pt}
\end{center}

% Education %
\section{EDUCATION}
\resumeSubHeadingListStart

\resumeSubheading
{Truman State University}{Aug. 2020 -- May 2023}
{Bachelor of Science in Computer Science, Minor in Business Administration}{Kirksville, MO}
{GPA: 3.4}
\resumeItemListStart
\resumeItem {\textbf{Coursework}: OOP and Design, Data Structures, Algorithm Analysis}
\resumeItem
{\textbf{Awards and Honors}: Truman President's Honorary Scholarship, Transfer Recognition Scholarship}
\resumeItemListEnd

\resumeSubheading
{Moberly Area Community College}{Aug. 2019 -- Jul. 2020}
{Associates of Arts in General Studies}{Moberly, MO}
{GPA: 3.5}
\resumeItemListStart
\resumeItem {\textbf{Coursework}: Public Speaking, Calculus and Trigonometry}
\resumeItem
{\textbf{Awards and Honors}: Missouri A+ Scholarship, President's List}
\resumeItemListEnd
\resumeSubHeadingListEnd

% Programming Skills %
\section{SKILLS}
\begin{itemize}[leftmargin=0in, label={}]
	\small{\item{
		\textbf{Proficient Languages} {: Java, C++11, C99}\vspace{2pt}
		\hfill
		\textbf{Familiar Languages} {: Javascript, Solidity, Python, C\#, Rust}\vspace{2pt} \\
		\textbf{Tools}     {: Git, Bash, Gradle, Maven, Make, CMake}
    \hfill
    \textbf{Environments and Libraries}     {: Windows, Linux, OpenGL, NodeJS}
	}}
\end{itemize}


% Work Experience %
\section{WORK EXPERIENCE}
\resumeSubHeadingListStart
\resumeSubheading
{Walmart}{Jun. 2019 -- Dec. 2019}
{Self Checkout Host}{Mexico, MO}
{}
\resumeItemListStart
\resumeItem{Interacted with numerous customers on a daily basis and answered any questions regarding the self checkout process}
\resumeItem{Assisted customers with any problems regarding the self checkout machines and machine software}
\resumeItem{Handled machine software and reported any bugs relating to said software}
\resumeItemListEnd
\resumeSubHeadingListEnd

% Projects %
\section{PROJECTS}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{Main Street Kirksville Website}} {Sept. 2019 -- Mar. 2021}
\resumeItemListStart
\resumeItem{\textbf{Fullstack developer and designer} of a non-profit organization website led by Truman ACM}
\resumeItem{Communicated within a team of fullstack developers and voiced agreements and concerns to fellow developers}
\resumeItem{Helped \textbf{design and implement} a catalog of local businesses in a table and a map of nearby parking spots}
\resumeItem{Used tools including \textbf{WordPress} and Google MyMaps to implement the website and website features}
\resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{OpenGL Project}} {Sept. 2019 -- Mar. 2021}
\resumeItemListStart
\resumeItem{Applied the graphics programming library OpenGL using \textbf{C++} to draw cubes and other shapes in a program}
\resumeItem{Learned matrices, vectors, and other linear algebraic techniques}
\resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{Tic-Tac-Toe AI}} {Sept. 2019 -- Mar. 2021}
\resumeItemListStart
\resumeItem{Implemented a tic-tac-toe game in \textbf{Java} using object-oriented programming techniques}
\resumeItem{Created an AI which would try to tie the game against a human opponent using the minimax algorithm}
\resumeItemListEnd
\resumeSubHeadingListEnd

% Extracurriculars %

\section{EXTRACURRICULARS}
\resumeSubHeadingListStart
\resumeExtracurricularsHeading
{\textbf{Association for Computing Machinery}}
\resumeItemListStart
\resumeItem{Collaborated with fellow members with various projects including research on blockchains}
\resumeItem{Participated in surveys and meetings to decide current and future endeavours for the organization}
\resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeExtracurricularsHeading
{\textbf{University Decentralized Autonomous Organization}}
\resumeItemListStart
\resumeItem{\textbf{Founded} an organization which promotes decentralization using a DAO, educating members along the way}
\resumeItem{Developed an in-house DAO from scratch using \textbf{NodeJS}, \textbf{Hardhat}, \textbf{Solidity}, and \textbf{React}}
\resumeItemListEnd
\resumeSubHeadingListEnd
\end{document}
